Methods to prioritise pop-up active transport infrastructure

### 2020-05-10 article.Rmd
Add important point that funding is not the only change. The associated guidance and legal changes are a culmination of 10 years of campaigning, and would not have happened without this.

Local and national governments are working out how best to respond.
Many options are available to ensure that citizens can benefit from outdoor activity while minimising health risks, ranging from the hand sanitiser provision to the creation of extra active transport space [@freeman_covid19_2020].
Installation of 'pop-up' active transport infrastructure has been endorsed and implemented in many places [@laker_world_2020].
The Scottish government, for example, has provided £10 million "to keep key workers moving" by "reallocating road space to better enable this shift and make it safer for people who choose to walk, cycle or wheel for essential trips or for exercise" [@transportscotland_10_2020].
On 9^th^ May 2020, the UK government announced a £250 million package for pop-up active transport infrastructure [@reid_government_2020].
Evidence is needed to ensure that such investment is spent effectively and where it is most needed.

>>>>

Local and national governments are working out how best to respond.
Many options are available to ensure that citizens can benefit from outdoor activity while minimising health risks, ranging from the hand sanitiser provision to the creation of extra active transport space [@freeman_covid19_2020].
Installation of 'pop-up' active transport infrastructure has been endorsed and implemented in many places [@laker_world_2020].
The Scottish government, for example, has provided £10 million "to keep key workers moving" by "reallocating road space to better enable this shift and make it safer for people who choose to walk, cycle or wheel for essential trips or for exercise" [@transportscotland_10_2020].
On 9^th^ May 2020, the UK government announced a £250 million package for pop-up active transport infrastructure [@reid_government_2020].
Significantly, alongside funding, this includes announcement of fast-tracking of long-awaited guidance, an updated Cycling and Walking Investment Strategy and legal changes to protect vulnerable road users [@govuk_transport-secretary_2020]. These are objectives that the cycling advocacy community has campaigned for over the last decade, with little progress.
Evidence is needed to ensure that such investment is spent effectively and where it is most needed.
